---
title: "Matching overview"
output: html_document
date: "`r Sys.Date()`"
params:
  df: NULL
  model_matched: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

stopifnot(!is.null(params$df))
stopifnot(!is.null(params$model_matched))
```

```{r calculations, echo = FALSE}

model_summary = summary(params$model_matched, un = FALSE)
balance_summary = as.data.frame(model_summary$sum.matched)

```

## Predictive model summary
Receiver Operating Characteristic (ROC) from the logit model

```{r logit, echo = FALSE}
roc = pROC::roc(params$df$to_match,params$df$predicted_prob)
cat("Area under the curve:", round(roc$auc, 4), "\n")
```

We expect scores > 0.9 in most cases.

## Matching model summary

### Model summary

```{r matching_summary, echo = FALSE}
print(model_summary$nn)
```

We expect:

1. most treated records to be matched
2. about twice as many control records to be matched
3. the remaining control records to be unmatched
4. minimal records to be discarded

### Observational balance

```{r matching_balance, echo = FALSE}
params$df |>
  dplyr::group_by(to_match, treat_control_other) |>
  dplyr::summarise(num = dplyr::n(), dist_uid = dplyr::n_distinct(snz_uid)) |>
  print()

```

We expect:

1. the `num` column to be consistent with the Model summary
2. the `dist_uid` column to be of a similar magnitude to the `num` column for control.

If the control row shows `dist_uid` is much smaller that `num`, then people used
for matching have been used on many of their possible reference dates. This may
lower the robustness of the method.

## Propensity scores before and after

Distribution of predicted probabilities prior to matching

```{r prior_density, echo = FALSE}
plot_data = dplyr::mutate(params$df, treat_control_other = ifelse(treat_control_other == "other", "control", treat_control_other))
ggplot2::ggplot(data = plot_data)+
  ggplot2::geom_density(ggplot2::aes(x = predicted_prob, colour = treat_control_other)) +
  ggplot2::scale_y_sqrt()
```

Distribution of predicted probabilities after matching

```{r after_density, echo = FALSE}
plot_data = dplyr::filter(params$df, treat_control_other != "other")
ggplot2::ggplot(data = plot_data) +
  ggplot2::geom_density(ggplot2::aes(x = predicted_prob, colour = treat_control_other)) +
  ggplot2::scale_y_sqrt()
```

We expect the control distribution before matching to show a heavy skew towards
zero, and for the two distributions after matching to appear much more similar.

## Love plot

This shows the quality of matching. Scores between 0 and 0.1 are considered well
matched. Scores between 0.1 and 0.2 are a poor match. Scores greater than 0.2
are not considered matched.

```{r love_plot, echo = FALSE, fig.height = 24}
plot(summary(model_matched), var.order = "matched")
```

As part of having a standardised method, and a large number of measures we have
to accept that not all measures will be well matched. But still important to
check for quality of matching. Take special note of measures that are key to
the description of the population.

## Data behind the love plot

Unmatched attributes

```{r love_data_1, echo = FALSE}
balance_summary |>
  dplyr::filter(abs(`Std. Mean Diff.`) > 0.2) |>
  dplyr::arrange(-abs(`Std. Mean Diff.`)) |>
  dplyr::select('Means Treated', 'Means Control', 'Std. Mean Diff.', 'Var. Ratio', 'Std. Pair Dist.') |>
  print()
```

Poor match attributes

```{r love_data_2, echo = FALSE}
balance_summary |>
  dplyr::filter(
    abs(`Std. Mean Diff.`) <= 0.2,
    abs(`Std. Mean Diff.`) > 0.1
  ) |>
  dplyr::arrange(-abs(`Std. Mean Diff.`)) |>
  dplyr::select('Means Treated', 'Means Control', 'Std. Mean Diff.', 'Var. Ratio', 'Std. Pair Dist.') |>
  print()
```

Good match attributes

```{r love_data_3, echo = FALSE}
balance_summary |>
  dplyr::filter(abs(`Std. Mean Diff.`) <= 0.1) |>
  dplyr::arrange(-abs(`Std. Mean Diff.`)) |>
  dplyr::select('Means Treated', 'Means Control', 'Std. Mean Diff.', 'Var. Ratio', 'Std. Pair Dist.') |>
  print()
```

